Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-22 paper/sections/introduction.tex
[ paper ] working on structurally smaller arguments.

A proof-reconstruction tool provides such an integration translating
the reply delivered by the prover into the formalism of the proof
assistant. Because the formalism of the source (the evidence
generated by the \ATP) is not necessarily the same logic in the
target, the reconstruction turns out in a ``reverse engineering''
task. Then, reconstructing a proof involves an in-depth
understanding of the algorithms in the \ATP and the specification
logic in the \ITP. To begin with the proof-reconstruction, it is
necessary to have a proof-object from the \ATP in a consistent
format to work with, that is, a full script describing step-by-step
with exhaustive details and without ambiguities, the derivation to
get the actual proof.
For problems in classical propositional logic (henceforth \CPL),
from a list of at least forty\footnote{\ATPs available from the web
service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few
provers were able to deliver proofs (e.g.,
\name{CVC4}~\cite{Barrett2011}, \name{SPASS}, and
\name{Waldmeister}~\cite{hillenbrand1997}) and a little bit less replied with a proof
in a file format like \TSTP~\cite{sutcliffe2004tstp} (e.g.,
\name{E}, \Metis, \name{Vampire}, and \name{Z3}),
\len{LFSC}~\cite{Stump2008}, or the \len{SMT-LIB}~\cite{Bohme2011} format.

>>>>

A proof-reconstruction tool provides such an integration translating
the reply delivered by the prover into the formalism of the proof
assistant. Because the formalism of the source (the evidence
generated by the \ATP) is not necessarily the same logic in the
target, the reconstruction turns out in a ``reverse engineering''
task. Then, reconstructing a proof involves an in-depth
understanding of the algorithms in the \ATP and the specification
logic in the \ITP. To begin with the proof-reconstruction, it is
necessary to have a proof-object from the \ATP in a consistent
format to work with, that is, a full script describing step-by-step
with exhaustive details and without ambiguities, the derivation to
get the actual proof.
For problems in classical propositional logic (henceforth \CPL),
from a list of at least forty\footnote{\ATPs available from the web
service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few
provers were able to deliver proofs (e.g.,
\name{CVC4}~\cite{Barrett2011}, \name{SPASS}, and
\name{Waldmeister}~\cite{hillenbrand1997}) and a little bit less replied with a proof
in a file format like \TSTP~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006} (e.g.,
\name{E}, \Metis, \name{Vampire}, and \name{Z3}),
\len{LFSC}~\cite{Stump2008}, or the \len{SMT-LIB}~\cite{Bohme2011} format.
